Kanwal (2017) BDA Notebook

### 2018-03-31 kanwal-analysis/BDA-analysis.Rmd
updated analysis on hueristic modelable subset

## BDA data
```{r generative-model}
fPath <- "../kanwal-generative-model-20180328.wppl"
m <- getModelFile(fPath)
```

Get posterior predictives...
```{r run-webppl}
dfSynthetic <- rwebppl::webppl(m)
```

@@

How do model predictions look compared to empirical data?
```{r plot-synthetic-vs-empirical}
dfEmpSynth %>%
  spread(display_type, prop) %>%
  ggplot(aes(x=frequent, y=infrequent, col=data_type, group=IP)) +
    geom_point(alpha=0.7, size=2) +
    geom_line(alpha=0.7, col='grey', lty=2) +
    theme_few() +
    facet_grid(~condition)
```

@@

>>>>

# BDA - Modeling participant data

Note: this analysis includes 85% of participants as I'm having trouble modeling what appears to be fairly random behaviors... See `analysis.ipynb` for more information.
```{r getModelableData}
# Hueristic modelable data
f_modelable_data <- "../modelable-data-20180330.csv"
dfModelable <- read.csv(f_modelable_data)

# All data
f_all_data <- "../kanwal-preprocessed.csv"
dfAll <- read.csv(f_all_data) %>%
  mutate(frequent=round(frequent, 2),
         infrequent=round(infrequent, 2))
```

```{r setup-bda-model}
f_bda_model <- "../kanwal-BDA-20180330.wppl"
model_bda <- getModelFile(f_bda_model)
bda_data <- head(dfModelable)
nrow(dfModelable)

x1 <- '115.98.55.114'
x2 <- '117.217.210.9'
# but worked on second time
dfAll2 <- dfAll %>% filter(IP != x2,
                           condition !='neither')
```

Note: slow running.
```{r run-bda-model}
# pt <- proc.time()
# df_bda <- rwebppl::webppl(model_bda, data=dfModelable, data_var='rData')
# et <- proc.time() - pt
# write.csv(df_bda, "bda-tuned-params-20180303.csv")
```

```{r optional-read-cached-data}
# If we haven't re-run the BDA predictives then load cached version.
if (!exists('df_bda')) {
  df_bda <- read.csv("bda-tuned-params-20180303.csv")
}
```

## BDA predictive
```{r generative-model}
fPath <- "../kanwal-generative-model-20180328.wppl"
m <- getModelFile(fPath)
```

Get posterior predictives...
```{r run-webppl}
dfSynthetic <- rwebppl::webppl(m, data=df_bda, data_var='rData')
```

@@

How do model predictions look compared to empirical data?
```{r plot-synthetic-vs-empirical}
dfEmpSynth %>%
  spread(display_type, prop) %>%
  ggplot(aes(x=frequent, y=infrequent, col=condition, group=IP)) +
    geom_point(aes(shape=data_type), alpha=0.5, size=2.5) +
    geom_line(alpha=0.7, col='grey', lty=2) +
    theme_few() +
    facet_grid(~condition)
```

@@

### Restricting analysis to rational scenarios...
```{r correlation-synthetic-vs-empirical-conditions}
dfEmpSynthCor <- dfEmpSynth  %>%
  filter(condition != 'neither') %>%
  spread(data_type, prop)

```{r plot-correlation-conditions}
dfEmpSynth %>%
  filter(condition != 'neither') %>%
  spread(data_type, prop) %>%
  ggplot(aes(x=synthetic, y=empirical)) +
    geom_jitter(aes(col=condition), alpha=0.5, width=0.01, height=0.01, size=2) +
    geom_smooth(method='lm') +
    ggtitle("Model vs Empirical predictions Kanwal (2017)") +
    theme_few() +
    theme(plot.title = element_text(hjust = 0.5))
```
